### 2017-04-06 paper/evaluation.tex
RQ6 - added dummmy data

\Fix{WIP}

>>>>

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 1.47m & 1.00x & 1.00x & 1.00x & 1.00x & 1.00x\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
\emph{Subject} & \emph{\# of tests} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
BounceStorage \textbf{Chaos} HTTP Proxy  & 8765 & 10\% & 10\% & 10\% & 10\% & 10\%\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de flakyness}}
\label{tab:rq6-efficiency}
\end{figure}
